RESEARCH PROPOSAL

### 2022-05-24 papers/fuzzy-fmt/OralExm-researchproposal.tex
oralexm another edit
oralexm edit

\section{Part 3: Research To Do}
\noindent %Toward a better model and a better understanding of our model, 
I propose some possible paths for wrapping up my research: \\
$\bullet$ Finish up the paper we have and graduate. \\
$\bullet$ Write a follow-on paper and graduate. In a second paper, I would 
like to look at finding the internal energy for our WCA fluid model using 
classical Density Functional Theory and our SFMT functional 
for the Helmholtz free energy that we developed in our first paper 
\begin{align}
  U[n(\vec r), s(\vec r)] = F[n(\vec r)] + T\int s(\vec r)
\end{align}
 If more is needed, or time allows, I could also: \\
$\bullet$ Look at how to improve results at low temperature, high density 
by adjusting our functional and/or potential and our pressure calculations.\\ %pressure calculations  \\
%$\bullet$ Possibly derive temperature-dependent parameter with B3 and B2  \\
%4- another functional for better pressure in freezing with improved pressure calculation\\
%4- another function (instead of Verf) for better pressure in freezing \\
$\bullet$ Examine and demonstrate the generality and usefulness of our 
method by applying it to other soft repulsive fluid potentials (Dr. Roundy famous!) \\
%$\bullet$ Apply our model  (ie. show by example) to demonstrate usefulness \\ %and market \\
%better understand and meet the needs of those who would benefit from our approach and market \\

>>>>

\section{Part 3: Research To Do}
\noindent %Toward a better model and a better understanding of our model, 
I propose some possible paths for wrapping up my research: \\
$\bullet$ Finish up the paper we have and graduate. \\
$\bullet$ Write a follow-on paper and graduate. In a second paper, I would 
like to look at finding the internal energy for our WCA fluid using 
classical Density Functional Theory and our SFMT functional 
for the Helmholtz free energy that we developed in our first paper 
\begin{align}
  U[n(\vec r), s(\vec r)] = F[n(\vec r)] + T\int s(\vec r) d\vec r
\end{align}
 Alternatively (or if more is needed, or time allows), I could: \\
$\bullet$ Look at how to improve results at low temperature, high density 
by adjusting our functional and/or potential and our pressure calculations.\\ %pressure calculations  \\
%$\bullet$ Possibly derive temperature-dependent parameter with B3 and B2  \\
%4- another functional for better pressure in freezing with improved pressure calculation\\
%4- another function (instead of Verf) for better pressure in freezing \\
$\bullet$ Examine and demonstrate the generality and usefulness of our 
method by applying it to other soft repulsive fluid potentials (Dr. Roundy famous!) \\
%$\bullet$ Apply our model  (ie. show by example) to demonstrate usefulness \\ %and market \\
%better understand and meet the needs of those who would benefit from our approach and market \\
